---
title: "Power vs. FDR plots for paper"
author: Yuxin Zou and Peter Carbonetto
output: workflowr::wflow_html
---

```{r knitr-opts, include=FALSE}
knitr::opts_chunk$set(comment = "#",collapse = TRUE,results = "hold",
                      fig.show = "hold",fig.align = "center",dpi = 120)
```

Load some packages used to create the power vs. FDR plots:

```{r load-pkgs, message=FALSE}
library(ggplot2)
library(cowplot)
```

Load the results from the UK Biobank simulations:

```{r load-results}
res0.005 = readRDS("data/roc_pve005.rds")
res0.1 = readRDS("data/roc_pve1.rds")
res0.3 = readRDS("data/roc_pve3.rds")
```


Create the power vs. PDR plot comparing refinement procedure with the 'in-sample' LD:
```{r refinement, fig.height=3, fig.width=4.5}
pdat <-
  rbind(data.frame(method = "without refinement",
                   fdr    = 1 - res0.005[["SuSiE-RSS-L10-refineFALSE-ERTRUE-LDin"]]$pr[,1],
                   power  = res0.005[["SuSiE-RSS-L10-refineFALSE-ERTRUE-LDin"]]$pr[,2],
                   thresh = res0.005[["SuSiE-RSS-L10-refineFALSE-ERTRUE-LDin"]]$pr[,3]),
        data.frame(method = "with refinement",
                   fdr    = 1 - res0.005[["SuSiE-RSS-L10-refineTRUE-ERTRUE-LDin"]]$pr[,1],
                   power  = res0.005[["SuSiE-RSS-L10-refineTRUE-ERTRUE-LDin"]]$pr[,2],
                   thresh = res0.005[["SuSiE-RSS-L10-refineTRUE-ERTRUE-LDin"]]$pr[,3]))
rows <- with(pdat,order(method,fdr))
pdat <- pdat[rows,]
p <- ggplot(pdat,aes(x = fdr,y = power,color = method,linetype = method)) +
  geom_line(orientation = "y") +
  geom_point(data = subset(pdat,thresh == 0.95),show.legend = FALSE) +
  scale_color_manual(values = c("orange","blue")) +
  scale_linetype_manual(values = c("solid","solid")) +
  scale_x_continuous(breaks = seq(0,0.3,0.05)) +
  scale_y_continuous(breaks = seq(0,0.3,0.05)) +
  coord_cartesian(xlim = c(0,0.3),ylim = c(0,0.3)) +
  theme_cowplot(font_size = 12) +
  theme(panel.grid.major = element_line(colour = "gainsboro",size = 0.3))
print(p)
```

```{r refinement-for-paper, echo=FALSE, message=FALSE}
ggsave("pip_power_vs_fdr_refine.eps",p,height=3,width=4.3)
```

Create the power vs. FDR plot comparing different fine-mapping methods
when they are provided with the "in sample" LD:

```{r in-sample, fig.height=5, fig.width=6}
pdat <-
  rbind(data.frame(method = "SuSiE-RSS, est sigma",
                   fdr    = 1 - res0.005[["SuSiE-RSS-L10-refineTRUE-ERTRUE-LDin"]]$pr[,1],
			       power  = res0.005[["SuSiE-RSS-L10-refineTRUE-ERTRUE-LDin"]]$pr[,2],
			       thresh = res0.005[["SuSiE-RSS-L10-refineTRUE-ERTRUE-LDin"]]$pr[,3]),
        data.frame(method = "SuSiE-RSS, sigma=1",
                   fdr    = 1 - res0.005[["SuSiE-RSS-L10-refineTRUE-ERFALSE-LDin"]]$pr[,1],
                   power  = res0.005[["SuSiE-RSS-L10-refineTRUE-ERFALSE-LDin"]]$pr[,2],
                   thresh = res0.005[["SuSiE-RSS-L10-refineTRUE-ERFALSE-LDin"]]$pr[,3]),
        data.frame(method = "SuSiE-RSS, sigma=1, L=true",
                   fdr    = 1-res0.005[["SuSiE-RSS-Ltrue-refineTRUE-ERFALSE-LDin"]]$pr[,1],
                   power  = res0.005[["SuSiE-RSS-Ltrue-refineTRUE-ERFALSE-LDin"]]$pr[,2],
                   thresh = res0.005[["SuSiE-RSS-Ltrue-refineTRUE-ERFALSE-LDin"]]$pr[,3]),
        data.frame(method = "FINEMAP",
                   fdr    = 1-res0.005[["FINEMAP-L5-LDin"]]$pr[,1],
                   power  = res0.005[["FINEMAP-L5-LDin"]]$pr[,2],
                   thresh = res0.005[["FINEMAP-L5-LDin"]]$pr[,3]), 
        data.frame(method = "FINEMAP, L=true",
                   fdr    = 1-res0.005[["FINEMAP-Loracle-LDin"]]$pr[,1],
                   power  = res0.005[["FINEMAP-Loracle-LDin"]]$pr[,2],
                   thresh = res0.005[["FINEMAP-Loracle-LDin"]]$pr[,3]),
        data.frame(method = "DAP-G",
                   fdr    = 1-res0.005[["DAP-G-LDin"]]$pr[,1],
                   power  = res0.005[["DAP-G-LDin"]]$pr[,2],
                   thresh = res0.005[["DAP-G-LDin"]]$pr[,3]),
        data.frame(method = "CAVIAR",
                   fdr    = 1-res0.005[["CAVIAR-LDin"]]$pr[,1],
                   power  = res0.005[["CAVIAR-LDin"]]$pr[,2],
                   thresh = res0.005[["CAVIAR-LDin"]]$pr[,3]))
rows <- with(pdat,order(method,fdr))
pdat <- pdat[rows,]
pdat$method = factor(pdat$method, levels = c('SuSiE-RSS, est sigma',
                                             'SuSiE-RSS, sigma=1','SuSiE-RSS, sigma=1, L=true',
                                             'FINEMAP', 'FINEMAP, L=true',
                                             'DAP-G', 'CAVIAR'))
p <- ggplot(pdat,aes(x = fdr,y = power,color = method,linetype = method)) +
  geom_line(orientation = "y") +
  geom_point(data = subset(pdat,thresh == 0.95),show.legend = FALSE) +
  scale_color_manual(values = c("black","magenta","magenta","darkorange",
                                "darkorange","dodgerblue","limegreen")) +
  scale_linetype_manual(values = c("dotted","solid","dashed","solid",
                                   "dashed","solid","solid")) +
  scale_x_continuous(breaks = seq(0,0.3,0.05)) +
  scale_y_continuous(breaks = seq(0,0.3,0.05)) +
  coord_cartesian(xlim = c(0,0.3),ylim = c(0,0.3)) +
  theme_cowplot(font_size = 12) +
  theme(panel.grid.major = element_line(colour = "gainsboro",size = 0.3))
print(p)
```

```{r in-sample-for-paper, echo=FALSE, message=FALSE}
ggsave("pip_power_vs_fdr_insample.eps",p,height=3,width=4.3)
```

Create the power vs. FDR plot comparing different fine-mapping methods
when they are provided with the "out of sample" LD:

```{r plots-comparing-all-methods, fig.height=7, fig.width=7}
pdat1 <-
  rbind(data.frame(method = "SuSiE-RSS (in-sample LD)",
                   fdr    = 1 - res0.005[["SuSiE-RSS-L10-refineTRUE-ERTRUE-LDin"]]$pr[,1],
			       power  = res0.005[["SuSiE-RSS-L10-refineTRUE-ERTRUE-LDin"]]$pr[,2],
			       thresh = res0.005[["SuSiE-RSS-L10-refineTRUE-ERTRUE-LDin"]]$pr[,3]),
        data.frame(method = "in-sample LD",
                   fdr    = 1 - res0.005[["CAVIAR-LDin"]]$pr[,1],
                   power  = res0.005[["CAVIAR-LDin"]]$pr[,2],
                   thresh = res0.005[["CAVIAR-LDin"]]$pr[,3]),
        data.frame(method = "n=1000,lambda=0",
                   fdr    = 1-res0.005[["CAVIAR-LDref1000"]]$pr[,1],
                   power  = res0.005[["CAVIAR-LDref1000"]]$pr[,2],
                   thresh = res0.005[["CAVIAR-LDref1000"]]$pr[,3]),
        data.frame(method = "n=1000,lambda=0.001",
                   fdr    = 1 - res0.005[["CAVIAR-LDref1000-lambda0.001"]]$pr[,1],
                   power  = res0.005[["CAVIAR-LDref1000-lambda0.001"]]$pr[,2],
                   thresh = res0.005[["CAVIAR-LDref1000-lambda0.001"]]$pr[,3]),
        data.frame(method = "n=1000,lambda=estimated",
                   fdr    = 1-res0.005[["CAVIAR-LDref1000-lambdaEstimate"]]$pr[,1],
                   power  = res0.005[["CAVIAR-LDref1000-lambdaEstimate"]]$pr[,2],
                   thresh = res0.005[["CAVIAR-LDref1000-lambdaEstimate"]]$pr[,3]),
        data.frame(method = "n=500,lambda=0",
                   fdr    = 1 - res0.005[["CAVIAR-LDref500"]]$pr[,1],
                   power  = res0.005[["CAVIAR-LDref500"]]$pr[,2],
                   thresh = res0.005[["CAVIAR-LDref500"]]$pr[,3]),
        data.frame(method = "n=500,lambda=0.001",
                   fdr    = 1 - res0.005[["CAVIAR-LDref500-lambda0.001"]]$pr[,1],
                   power  = res0.005[["CAVIAR-LDref500-lambda0.001"]]$pr[,2],
                   thresh = res0.005[["CAVIAR-LDref500-lambda0.001"]]$pr[,3]),
        data.frame(method = "n=500,lambda=estimated",
                   fdr    = 1 - res0.005[["CAVIAR-LDref500-lambdaEstimate"]]$pr[,1],
                   power  = res0.005[["CAVIAR-LDref500-lambdaEstimate"]]$pr[,2],
                   thresh = res0.005[["CAVIAR-LDref500-lambdaEstimate"]]$pr[,3]))
pdat2 <-
  rbind(data.frame(method = "SuSiE-RSS (in-sample LD)",
                   fdr    = 1 - res0.005[["SuSiE-RSS-L10-refineTRUE-ERTRUE-LDin"]]$pr[,1],
			       power  = res0.005[["SuSiE-RSS-L10-refineTRUE-ERTRUE-LDin"]]$pr[,2],
			       thresh = res0.005[["SuSiE-RSS-L10-refineTRUE-ERTRUE-LDin"]]$pr[,3]),
        data.frame(method = "in-sample LD",
                   fdr    = 1 - res0.005[["DAP-G-LDin"]]$pr[,1],
                   power  = res0.005[["DAP-G-LDin"]]$pr[,2],
                   thresh = res0.005[["DAP-G-LDin"]]$pr[,3]),
        data.frame(method = "n=1000,lambda=0",
                   fdr    = 1-res0.005[["DAP-G-LDref1000"]]$pr[,1],
                   power  = res0.005[["DAP-G-LDref1000"]]$pr[,2],
                   thresh = res0.005[["DAP-G-LDref1000"]]$pr[,3]),
        data.frame(method = "n=1000,lambda=0.001",
                   fdr    = 1 - res0.005[["DAP-G-LDref1000-lambda0.001"]]$pr[,1],
                   power  = res0.005[["DAP-G-LDref1000-lambda0.001"]]$pr[,2],
                   thresh = res0.005[["DAP-G-LDref1000-lambda0.001"]]$pr[,3]),
        data.frame(method = "n=1000,lambda=estimated",
                   fdr    = 1-res0.005[["DAP-G-LDref1000-lambdaEstimate"]]$pr[,1],
                   power  = res0.005[["DAP-G-LDref1000-lambdaEstimate"]]$pr[,2],
                   thresh = res0.005[["DAP-G-LDref1000-lambdaEstimate"]]$pr[,3]),
        data.frame(method = "n=500,lambda=0",
                   fdr    = 1 - res0.005[["DAP-G-LDref500"]]$pr[,1],
                   power  = res0.005[["DAP-G-LDref500"]]$pr[,2],
                   thresh = res0.005[["DAP-G-LDref500"]]$pr[,3]),
        data.frame(method = "n=500,lambda=0.001",
                   fdr    = 1 - res0.005[["DAP-G-LDref500-lambda0.001"]]$pr[,1],
                   power  = res0.005[["DAP-G-LDref500-lambda0.001"]]$pr[,2],
                   thresh = res0.005[["DAP-G-LDref500-lambda0.001"]]$pr[,3]),
        data.frame(method = "n=500,lambda=estimated",
                   fdr    = 1 - res0.005[["DAP-G-LDref500-lambdaEstimate"]]$pr[,1],
                   power  = res0.005[["DAP-G-LDref500-lambdaEstimate"]]$pr[,2],
                   thresh = res0.005[["DAP-G-LDref500-lambdaEstimate"]]$pr[,3]))
pdat3 <-
  rbind(data.frame(method = "SuSiE-RSS (in-sample LD)",
                   fdr    = 1 - res0.005[["SuSiE-RSS-L10-refineTRUE-ERTRUE-LDin"]]$pr[,1],
			       power  = res0.005[["SuSiE-RSS-L10-refineTRUE-ERTRUE-LDin"]]$pr[,2],
			       thresh = res0.005[["SuSiE-RSS-L10-refineTRUE-ERTRUE-LDin"]]$pr[,3]),
        data.frame(method = "in-sample LD",
                   fdr    = 1 - res0.005[["FINEMAP-Loracle-LDin"]]$pr[,1],
                   power  = res0.005[["FINEMAP-Loracle-LDin"]]$pr[,2],
                   thresh = res0.005[["FINEMAP-Loracle-LDin"]]$pr[,3]),
        data.frame(method = "n=1000,lambda=0",
                   fdr    = 1-res0.005[["FINEMAP-Loracle-LDref1000"]]$pr[,1],
                   power  = res0.005[["FINEMAP-Loracle-LDref1000"]]$pr[,2],
                   thresh = res0.005[["FINEMAP-Loracle-LDref1000"]]$pr[,3]),
        data.frame(method = "n=1000,lambda=0.001",
                   fdr    = 1 - res0.005[["FINEMAP-Loracle-LDref1000-lambda0.001"]]$pr[,1],
                   power  = res0.005[["FINEMAP-Loracle-LDref1000-lambda0.001"]]$pr[,2],
                   thresh = res0.005[["FINEMAP-Loracle-LDref1000-lambda0.001"]]$pr[,3]),
        data.frame(method = "n=1000,lambda=estimated",
                   fdr    = 1-res0.005[["FINEMAP-Loracle-LDref1000-lambdaEstimate"]]$pr[,1],
                   power  = res0.005[["FINEMAP-Loracle-LDref1000-lambdaEstimate"]]$pr[,2],
                   thresh = res0.005[["FINEMAP-Loracle-LDref1000-lambdaEstimate"]]$pr[,3]),
        data.frame(method = "n=500,lambda=0",
                   fdr    = 1 - res0.005[["FINEMAP-Loracle-LDref500"]]$pr[,1],
                   power  = res0.005[["FINEMAP-Loracle-LDref500"]]$pr[,2],
                   thresh = res0.005[["FINEMAP-Loracle-LDref500"]]$pr[,3]),
        data.frame(method = "n=500,lambda=0.001",
                   fdr    = 1 - res0.005[["FINEMAP-Loracle-LDref500-lambda0.001"]]$pr[,1],
                   power  = res0.005[["FINEMAP-Loracle-LDref500-lambda0.001"]]$pr[,2],
                   thresh = res0.005[["FINEMAP-Loracle-LDref500-lambda0.001"]]$pr[,3]),
        data.frame(method = "n=500,lambda=estimated",
                   fdr    = 1 - res0.005[["FINEMAP-Loracle-LDref500-lambdaEstimate"]]$pr[,1],
                   power  = res0.005[["FINEMAP-Loracle-LDref500-lambdaEstimate"]]$pr[,2],
                   thresh = res0.005[["FINEMAP-Loracle-LDref500-lambdaEstimate"]]$pr[,3]))
pdat4 <-
  rbind(data.frame(method = "SuSiE-RSS (in-sample LD)",
                   fdr    = 1 - res0.005[["SuSiE-RSS-L10-refineTRUE-ERTRUE-LDin"]]$pr[,1],
			       power  = res0.005[["SuSiE-RSS-L10-refineTRUE-ERTRUE-LDin"]]$pr[,2],
			       thresh = res0.005[["SuSiE-RSS-L10-refineTRUE-ERTRUE-LDin"]]$pr[,3]),
        data.frame(method = "in-sample LD",
                   fdr    = 1 - res0.005[["FINEMAP-L5-LDin"]]$pr[,1],
                   power  = res0.005[["FINEMAP-L5-LDin"]]$pr[,2],
                   thresh = res0.005[["FINEMAP-L5-LDin"]]$pr[,3]),
        data.frame(method = "n=1000,lambda=0",
                   fdr    = 1-res0.005[["FINEMAP-L5-LDref1000"]]$pr[,1],
                   power  = res0.005[["FINEMAP-L5-LDref1000"]]$pr[,2],
                   thresh = res0.005[["FINEMAP-L5-LDref1000"]]$pr[,3]),
        data.frame(method = "n=1000,lambda=0.001",
                   fdr    = 1 - res0.005[["FINEMAP-L5-LDref1000-lambda0.001"]]$pr[,1],
                   power  = res0.005[["FINEMAP-L5-LDref1000-lambda0.001"]]$pr[,2],
                   thresh = res0.005[["FINEMAP-L5-LDref1000-lambda0.001"]]$pr[,3]),
        data.frame(method = "n=1000,lambda=estimated",
                   fdr    = 1-res0.005[["FINEMAP-L5-LDref1000-lambdaEstimate"]]$pr[,1],
                   power  = res0.005[["FINEMAP-L5-LDref1000-lambdaEstimate"]]$pr[,2],
                   thresh = res0.005[["FINEMAP-L5-LDref1000-lambdaEstimate"]]$pr[,3]),
        data.frame(method = "n=500,lambda=0",
                   fdr    = 1 - res0.005[["FINEMAP-L5-LDref500"]]$pr[,1],
                   power  = res0.005[["FINEMAP-L5-LDref500"]]$pr[,2],
                   thresh = res0.005[["FINEMAP-L5-LDref500"]]$pr[,3]),
        data.frame(method = "n=500,lambda=0.001",
                   fdr    = 1 - res0.005[["FINEMAP-L5-LDref500-lambda0.001"]]$pr[,1],
                   power  = res0.005[["FINEMAP-L5-LDref500-lambda0.001"]]$pr[,2],
                   thresh = res0.005[["FINEMAP-L5-LDref500-lambda0.001"]]$pr[,3]),
        data.frame(method = "n=500,lambda=estimated",
                   fdr    = 1 - res0.005[["FINEMAP-L5-LDref500-lambdaEstimate"]]$pr[,1],
                   power  = res0.005[["FINEMAP-L5-LDref500-lambdaEstimate"]]$pr[,2],
                   thresh = res0.005[["FINEMAP-L5-LDref500-lambdaEstimate"]]$pr[,3]))
pdat5 <-
  rbind(data.frame(method = "SuSiE-RSS (in-sample LD)",
                   fdr    = 1 - res0.005[["SuSiE-RSS-L10-refineTRUE-ERTRUE-LDin"]]$pr[,1],
			       power  = res0.005[["SuSiE-RSS-L10-refineTRUE-ERTRUE-LDin"]]$pr[,2],
			       thresh = res0.005[["SuSiE-RSS-L10-refineTRUE-ERTRUE-LDin"]]$pr[,3]),
        data.frame(method = "in-sample LD",
                   fdr    = 1 - res0.005[["SuSiE-RSS-Ltrue-refineTRUE-ERFALSE-LDin"]]$pr[,1],
                   power  = res0.005[["SuSiE-RSS-Ltrue-refineTRUE-ERFALSE-LDin"]]$pr[,2],
                   thresh = res0.005[["SuSiE-RSS-Ltrue-refineTRUE-ERFALSE-LDin"]]$pr[,3]),
        data.frame(method = "n=1000,lambda=0",
                   fdr    = 1-res0.005[["SuSiE-RSS-Ltrue-refineTRUE-ERFALSE-LDref1000"]]$pr[,1],
                   power  = res0.005[["SuSiE-RSS-Ltrue-refineTRUE-ERFALSE-LDref1000"]]$pr[,2],
                   thresh = res0.005[["SuSiE-RSS-Ltrue-refineTRUE-ERFALSE-LDref1000"]]$pr[,3]),
        data.frame(method = "n=1000,lambda=0.001",
                   fdr    = 1 - res0.005[["SuSiE-RSS-Ltrue-refineTRUE-ERFALSE-LDref1000-lambda0.001"]]$pr[,1],
                   power  = res0.005[["SuSiE-RSS-Ltrue-refineTRUE-ERFALSE-LDref1000-lambda0.001"]]$pr[,2],
                   thresh = res0.005[["SuSiE-RSS-Ltrue-refineTRUE-ERFALSE-LDref1000-lambda0.001"]]$pr[,3]),
        data.frame(method = "n=1000,lambda=estimated",
                   fdr    = 1-res0.005[["SuSiE-RSS-Ltrue-refineTRUE-ERFALSE-LDref1000-lambdaEstimate"]]$pr[,1],
                   power  = res0.005[["SuSiE-RSS-Ltrue-refineTRUE-ERFALSE-LDref1000-lambdaEstimate"]]$pr[,2],
                   thresh = res0.005[["SuSiE-RSS-Ltrue-refineTRUE-ERFALSE-LDref1000-lambdaEstimate"]]$pr[,3]),
        data.frame(method = "n=500,lambda=0",
                   fdr    = 1 - res0.005[["SuSiE-RSS-Ltrue-refineTRUE-ERFALSE-LDref500"]]$pr[,1],
                   power  = res0.005[["SuSiE-RSS-Ltrue-refineTRUE-ERFALSE-LDref500"]]$pr[,2],
                   thresh = res0.005[["SuSiE-RSS-Ltrue-refineTRUE-ERFALSE-LDref500"]]$pr[,3]),
        data.frame(method = "n=500,lambda=0.001",
                   fdr    = 1 - res0.005[["SuSiE-RSS-Ltrue-refineTRUE-ERFALSE-LDref500-lambda0.001"]]$pr[,1],
                   power  = res0.005[["SuSiE-RSS-Ltrue-refineTRUE-ERFALSE-LDref500-lambda0.001"]]$pr[,2],
                   thresh = res0.005[["SuSiE-RSS-Ltrue-refineTRUE-ERFALSE-LDref500-lambda0.001"]]$pr[,3]),
        data.frame(method = "n=500,lambda=estimated",
                   fdr    = 1 - res0.005[["SuSiE-RSS-Ltrue-refineTRUE-ERFALSE-LDref500-lambdaEstimate"]]$pr[,1],
                   power  = res0.005[["SuSiE-RSS-Ltrue-refineTRUE-ERFALSE-LDref500-lambdaEstimate"]]$pr[,2],
                   thresh = res0.005[["SuSiE-RSS-Ltrue-refineTRUE-ERFALSE-LDref500-lambdaEstimate"]]$pr[,3]))
pdat6 <-
  rbind(data.frame(method = "SuSiE-RSS (in-sample LD)",
                   fdr    = 1 - res0.005[["SuSiE-RSS-L10-refineTRUE-ERTRUE-LDin"]]$pr[,1],
			       power  = res0.005[["SuSiE-RSS-L10-refineTRUE-ERTRUE-LDin"]]$pr[,2],
			       thresh = res0.005[["SuSiE-RSS-L10-refineTRUE-ERTRUE-LDin"]]$pr[,3]),
        data.frame(method = "in-sample LD",
                   fdr    = 1 - res0.005[["SuSiE-RSS-L10-refineTRUE-ERFALSE-LDin"]]$pr[,1],
                   power  = res0.005[["SuSiE-RSS-L10-refineTRUE-ERFALSE-LDin"]]$pr[,2],
                   thresh = res0.005[["SuSiE-RSS-L10-refineTRUE-ERFALSE-LDin"]]$pr[,3]),
        data.frame(method = "n=1000,lambda=0",
                   fdr    = 1-res0.005[["SuSiE-RSS-L10-refineTRUE-ERFALSE-LDref1000"]]$pr[,1],
                   power  = res0.005[["SuSiE-RSS-L10-refineTRUE-ERFALSE-LDref1000"]]$pr[,2],
                   thresh = res0.005[["SuSiE-RSS-L10-refineTRUE-ERFALSE-LDref1000"]]$pr[,3]),
        data.frame(method = "n=1000,lambda=0.001",
                   fdr    = 1 - res0.005[["SuSiE-RSS-L10-refineTRUE-ERFALSE-LDref1000-lambda0.001"]]$pr[,1],
                   power  = res0.005[["SuSiE-RSS-L10-refineTRUE-ERFALSE-LDref1000-lambda0.001"]]$pr[,2],
                   thresh = res0.005[["SuSiE-RSS-L10-refineTRUE-ERFALSE-LDref1000-lambda0.001"]]$pr[,3]),
        data.frame(method = "n=1000,lambda=estimated",
                   fdr    = 1-res0.005[["SuSiE-RSS-L10-refineTRUE-ERFALSE-LDref1000-lambdaEstimate"]]$pr[,1],
                   power  = res0.005[["SuSiE-RSS-L10-refineTRUE-ERFALSE-LDref1000-lambdaEstimate"]]$pr[,2],
                   thresh = res0.005[["SuSiE-RSS-L10-refineTRUE-ERFALSE-LDref1000-lambdaEstimate"]]$pr[,3]),
        data.frame(method = "n=500,lambda=0",
                   fdr    = 1 - res0.005[["SuSiE-RSS-L10-refineTRUE-ERFALSE-LDref500"]]$pr[,1],
                   power  = res0.005[["SuSiE-RSS-L10-refineTRUE-ERFALSE-LDref500"]]$pr[,2],
                   thresh = res0.005[["SuSiE-RSS-L10-refineTRUE-ERFALSE-LDref500"]]$pr[,3]),
        data.frame(method = "n=500,lambda=0.001",
                   fdr    = 1 - res0.005[["SuSiE-RSS-L10-refineTRUE-ERFALSE-LDref500-lambda0.001"]]$pr[,1],
                   power  = res0.005[["SuSiE-RSS-L10-refineTRUE-ERFALSE-LDref500-lambda0.001"]]$pr[,2],
                   thresh = res0.005[["SuSiE-RSS-L10-refineTRUE-ERFALSE-LDref500-lambda0.001"]]$pr[,3]),
        data.frame(method = "n=500,lambda=estimated",
                   fdr    = 1 - res0.005[["SuSiE-RSS-L10-refineTRUE-ERFALSE-LDref500-lambdaEstimate"]]$pr[,1],
                   power  = res0.005[["SuSiE-RSS-L10-refineTRUE-ERFALSE-LDref500-lambdaEstimate"]]$pr[,2],
                   thresh = res0.005[["SuSiE-RSS-L10-refineTRUE-ERFALSE-LDref500-lambdaEstimate"]]$pr[,3]))
pdat <- rbind(cbind(row = 1,col = 1,pdat1),
              cbind(row = 1,col = 2,pdat2),
			  cbind(row = 2,col = 1,pdat3),
			  cbind(row = 2,col = 2,pdat4),
			  cbind(row = 3,col = 1,pdat5),
			  cbind(row = 3,col = 2,pdat6))
rows <- with(pdat,order(row,col,method,fdr))
pdat <- pdat[rows,]
pdat$method = factor(pdat$method, levels = c('SuSiE-RSS (in-sample LD)',
                                             'in-sample LD',
                                             'n=1000,lambda=0',
                                             'n=1000,lambda=0.001', 
                                             'n=1000,lambda=estimated',
                                             'n=500,lambda=0',
                                             'n=500,lambda=0.001',
                                             'n=500,lambda=estimated'))
p <- ggplot(pdat,aes(x = fdr,y = power,color = method,linetype = method,
                     size = method)) +
  facet_grid(rows = vars(row),cols = vars(col)) +
  geom_line(orientation = "y") +
  geom_point(data = subset(pdat,thresh == 0.95),
             mapping = aes(x = fdr,y = power,color = method),
             inherit.aes = FALSE,show.legend = FALSE) +
  scale_color_manual(values = c("black","darkorange","royalblue","royalblue",
                                "royalblue","limegreen","limegreen",
								"limegreen")) +
  scale_linetype_manual(values = c("dotted","solid","solid","dotted","solid",
                                   "solid","dotted","solid")) +
  scale_size_manual(values = c(0.75,0.75,0.3,0.75,0.75,0.3,0.75,0.75)) +
  scale_x_continuous(breaks = seq(0,0.3,0.05)) +
  scale_y_continuous(breaks = seq(0,0.3,0.05)) +
  coord_cartesian(xlim = c(0,0.3),ylim = c(0,0.3)) +
  theme_cowplot(font_size = 10) +
  theme(panel.grid.major = element_line(colour = "gainsboro",size = 0.3))
print(p)
```

```{r plots-comparing-all-methods-for-paper, echo=FALSE, message=FALSE}
ggsave("pip_power_vs_fdr_outofsample.eps",p,height=7,width=6.75)
```

Create the power vs. FDR plot comparing different fine-mapping methods
when they are provided with the "out of sample" LD with higher PVE:

```{r higher-pve, fig.height=5, fig.width=15}
pdat1 <-
  rbind(data.frame(method = "SuSiE-RSS, est sigma (in-sample LD)",
                   fdr    = 1 - res0.005[["SuSiE-RSS-L10-refineTRUE-ERTRUE-LDin"]]$pr[,1],
			       power  = res0.005[["SuSiE-RSS-L10-refineTRUE-ERTRUE-LDin"]]$pr[,2],
			       thresh = res0.005[["SuSiE-RSS-L10-refineTRUE-ERTRUE-LDin"]]$pr[,3]),
        data.frame(method = "SuSiE-RSS, sigma=1",
                   fdr    = 1 - res0.005[["SuSiE-RSS-L10-refineTRUE-ERFALSE-LDref1000"]]$pr[,1],
                   power  = res0.005[["SuSiE-RSS-L10-refineTRUE-ERFALSE-LDref1000"]]$pr[,2],
                   thresh = res0.005[["SuSiE-RSS-L10-refineTRUE-ERFALSE-LDref1000"]]$pr[,3]),
        data.frame(method = "SuSiE-RSS, sigma=1, L=TRUE",
                   fdr    = 1-res0.005[["SuSiE-RSS-Ltrue-refineTRUE-ERFALSE-LDref1000"]]$pr[,1],
                   power  = res0.005[["SuSiE-RSS-Ltrue-refineTRUE-ERFALSE-LDref1000"]]$pr[,2],
                   thresh = res0.005[["SuSiE-RSS-Ltrue-refineTRUE-ERFALSE-LDref1000"]]$pr[,3]),
        data.frame(method = "FINEMAP",
                   fdr    = 1 - res0.005[["FINEMAP-L5-LDref1000"]]$pr[,1],
                   power  = res0.005[["FINEMAP-L5-LDref1000"]]$pr[,2],
                   thresh = res0.005[["FINEMAP-L5-LDref1000"]]$pr[,3]),
        data.frame(method = "FINEMAP, L=TRUE",
                   fdr    = 1-res0.005[["FINEMAP-Loracle-LDref1000"]]$pr[,1],
                   power  = res0.005[["FINEMAP-Loracle-LDref1000"]]$pr[,2],
                   thresh = res0.005[["FINEMAP-Loracle-LDref1000"]]$pr[,3]),
        data.frame(method = "DAP-G",
                   fdr    = 1 - res0.005[["DAP-G-LDref1000"]]$pr[,1],
                   power  = res0.005[["DAP-G-LDref1000"]]$pr[,2],
                   thresh = res0.005[["DAP-G-LDref1000"]]$pr[,3]),
        data.frame(method = "CAVIAR",
                   fdr    = 1 - res0.005[["CAVIAR-LDref1000"]]$pr[,1],
                   power  = res0.005[["CAVIAR-LDref1000"]]$pr[,2],
                   thresh = res0.005[["CAVIAR-LDref1000"]]$pr[,3]))
pdat2 <-
  rbind(data.frame(method = "SuSiE-RSS, est sigma (in-sample LD)",
                   fdr    = 1 - res0.1[["SuSiE-RSS-L10-refineTRUE-ERTRUE-LDin"]]$pr[,1],
			       power  = res0.1[["SuSiE-RSS-L10-refineTRUE-ERTRUE-LDin"]]$pr[,2],
			       thresh = res0.1[["SuSiE-RSS-L10-refineTRUE-ERTRUE-LDin"]]$pr[,3]),
        data.frame(method = "SuSiE-RSS, sigma=1",
                   fdr    = 1 - res0.1[["SuSiE-RSS-L10-refineTRUE-ERFALSE-LDref1000"]]$pr[,1],
                   power  = res0.1[["SuSiE-RSS-L10-refineTRUE-ERFALSE-LDref1000"]]$pr[,2],
                   thresh = res0.1[["SuSiE-RSS-L10-refineTRUE-ERFALSE-LDref1000"]]$pr[,3]),
        data.frame(method = "SuSiE-RSS, sigma=1, L=TRUE",
                   fdr    = 1-res0.1[["SuSiE-RSS-Ltrue-refineTRUE-ERFALSE-LDref1000"]]$pr[,1],
                   power  = res0.1[["SuSiE-RSS-Ltrue-refineTRUE-ERFALSE-LDref1000"]]$pr[,2],
                   thresh = res0.1[["SuSiE-RSS-Ltrue-refineTRUE-ERFALSE-LDref1000"]]$pr[,3]),
        data.frame(method = "FINEMAP",
                   fdr    = 1 - res0.1[["FINEMAP-L5-LDref1000"]]$pr[,1],
                   power  = res0.1[["FINEMAP-L5-LDref1000"]]$pr[,2],
                   thresh = res0.1[["FINEMAP-L5-LDref1000"]]$pr[,3]),
        data.frame(method = "FINEMAP, L=TRUE",
                   fdr    = 1-res0.1[["FINEMAP-Loracle-LDref1000"]]$pr[,1],
                   power  = res0.1[["FINEMAP-Loracle-LDref1000"]]$pr[,2],
                   thresh = res0.1[["FINEMAP-Loracle-LDref1000"]]$pr[,3]),
        data.frame(method = "DAP-G",
                   fdr    = 1 - res0.1[["DAP-G-LDref1000"]]$pr[,1],
                   power  = res0.1[["DAP-G-LDref1000"]]$pr[,2],
                   thresh = res0.1[["DAP-G-LDref1000"]]$pr[,3]),
        data.frame(method = "CAVIAR",
                   fdr    = 1 - res0.1[["CAVIAR-LDref1000"]]$pr[,1],
                   power  = res0.1[["CAVIAR-LDref1000"]]$pr[,2],
                   thresh = res0.1[["CAVIAR-LDref1000"]]$pr[,3]))
pdat3 <-
  rbind(data.frame(method = "SuSiE-RSS, est sigma (in-sample LD)",
                   fdr    = 1 - res0.3[["SuSiE-RSS-L10-refineTRUE-ERTRUE-LDin"]]$pr[,1],
			       power  = res0.3[["SuSiE-RSS-L10-refineTRUE-ERTRUE-LDin"]]$pr[,2],
			       thresh = res0.3[["SuSiE-RSS-L10-refineTRUE-ERTRUE-LDin"]]$pr[,3]),
        data.frame(method = "SuSiE-RSS, sigma=1",
                   fdr    = 1 - res0.3[["SuSiE-RSS-L10-refineTRUE-ERFALSE-LDref1000"]]$pr[,1],
                   power  = res0.3[["SuSiE-RSS-L10-refineTRUE-ERFALSE-LDref1000"]]$pr[,2],
                   thresh = res0.3[["SuSiE-RSS-L10-refineTRUE-ERFALSE-LDref1000"]]$pr[,3]),
        data.frame(method = "SuSiE-RSS, sigma=1, L=TRUE",
                   fdr    = 1-res0.3[["SuSiE-RSS-Ltrue-refineTRUE-ERFALSE-LDref1000"]]$pr[,1],
                   power  = res0.3[["SuSiE-RSS-Ltrue-refineTRUE-ERFALSE-LDref1000"]]$pr[,2],
                   thresh = res0.3[["SuSiE-RSS-Ltrue-refineTRUE-ERFALSE-LDref1000"]]$pr[,3]),
        data.frame(method = "FINEMAP",
                   fdr    = 1 - res0.3[["FINEMAP-L5-LDref1000"]]$pr[,1],
                   power  = res0.3[["FINEMAP-L5-LDref1000"]]$pr[,2],
                   thresh = res0.3[["FINEMAP-L5-LDref1000"]]$pr[,3]),
        data.frame(method = "FINEMAP, L=TRUE",
                   fdr    = 1-res0.3[["FINEMAP-Loracle-LDref1000"]]$pr[,1],
                   power  = res0.3[["FINEMAP-Loracle-LDref1000"]]$pr[,2],
                   thresh = res0.3[["FINEMAP-Loracle-LDref1000"]]$pr[,3]),
        data.frame(method = "DAP-G",
                   fdr    = 1 - res0.3[["DAP-G-LDref1000"]]$pr[,1],
                   power  = res0.3[["DAP-G-LDref1000"]]$pr[,2],
                   thresh = res0.3[["DAP-G-LDref1000"]]$pr[,3]),
        data.frame(method = "CAVIAR",
                   fdr    = 1 - res0.3[["CAVIAR-LDref1000"]]$pr[,1],
                   power  = res0.3[["CAVIAR-LDref1000"]]$pr[,2],
                   thresh = res0.3[["CAVIAR-LDref1000"]]$pr[,3]))
pdat <- rbind(cbind(row = 1,col = 0.005,pdat1),
              cbind(row = 1,col = 0.1,pdat2),
              cbind(row = 1,col = 0.3,pdat3))
rows <- with(pdat,order(row,col,method,fdr))
pdat <- pdat[rows,]
pdat$method = factor(pdat$method, levels = c('SuSiE-RSS, est sigma (in-sample LD)',
                                             'SuSiE-RSS, sigma=1',
                                             'SuSiE-RSS, sigma=1, L=TRUE',
                                             'FINEMAP', 
                                             'FINEMAP, L=TRUE',
                                             'DAP-G',
                                             'CAVIAR'))
p <- ggplot(pdat,aes(x = fdr,y = power,color = method,linetype = method)) +
  facet_grid(rows = vars(row),cols = vars(col)) +
  geom_line(orientation = "y") +
  geom_point(data = subset(pdat,thresh == 0.95),
             mapping = aes(x = fdr,y = power,color = method),
             inherit.aes = FALSE,show.legend = FALSE) +
  scale_color_manual(values = c("black","magenta","magenta","darkorange","darkorange",
                                "royalblue","limegreen")) +
  scale_linetype_manual(values = c("dotted","solid",'dashed',"solid","dashed",
                                   "solid","solid")) +
  scale_x_continuous(breaks = seq(0,0.3,0.05)) +
  scale_y_continuous(breaks = seq(0,0.3,0.05)) +
  coord_cartesian(xlim = c(0,0.3),ylim = c(0,0.3)) +
  theme_cowplot(font_size = 10) +
  theme(panel.grid.major = element_line(colour = "gainsboro",size = 0.3))
print(p)
```

```{r higher-pve-for-paper, echo=FALSE, message=FALSE}
ggsave("pip_power_vs_fdr_pve.eps",p,height=7,width=6.75)
```
