---
title: "SuSiE RSS convergence problem"
author: "Yuxin Zou"
date: "3/9/2021"
output: 
  workflowr::wflow_html:
    code_folding: hide
---

We observe the convergence problem for SuSiE in simulation.

```{r}
library(susieR)
dat = readRDS('data/susie_convergence_problem6.rds')
```

## Data 1

Default initialization doesn't work. LASSO initialization works.

```{r}
d1 = dat$d1
b = d1$true_coef
idx = which(b!=0)

par(mfrow=c(1,2))
plot(d1$z, pch = 16, xlab = 'SNPs', ylab = 'z')
points(idx, d1$z[idx], col='red', pch = 16)
log10p = -log10(pnorm(-abs(d1$z))*2)
plot(log10p, pch = 16, xlab = 'SNPs', ylab = '-log10 p value')
points(idx, log10p[idx], col='red', pch = 16)
```

With default initialization:
```{r}
f1 = susie_suff_stat(XtX = d1$XtX, Xty = d1$Xty, yty = d1$yty, n = d1$n, L=10)
susie_plot(f1, y='PIP', b=b, add_legend = T, main=paste0('ELBO: ', round(susie_get_objective(f1), 4)))
```
```{r}
f1 = susie_suff_stat(XtX = d1$XtX, Xty = d1$Xty, yty = d1$yty, n = d1$n, L=10, refine = TRUE)
susie_plot(f1, y='PIP', b=b, add_legend = T, main=paste0('ELBO: ', round(susie_get_objective(f1), 4)))

```


## Data 2

Default initialization doesn't work. LASSO initialization doesn't work.

```{r}
d2 = dat$d2
b = d2$true_coef
idx = which(b!=0)

par(mfrow=c(1,2))
plot(d2$z, pch = 16, xlab = 'SNPs', ylab = 'z')
points(idx, d2$z[idx], col='red', pch = 16)
log10p = -log10(pnorm(-abs(d2$z))*2)
plot(log10p, pch = 16, xlab = 'SNPs', ylab = '-log10 p value')
points(idx, log10p[idx], col='red', pch = 16)
```

With default initialization:
```{r}
f2 = susie_suff_stat(XtX = d2$XtX, Xty = d2$Xty, yty = d2$yty, n = d2$n, L=10, track_fit = T)
susie_plot(f2, y='PIP', b=b, add_legend = T, main=paste0('ELBO: ', round(susie_get_objective(f2), 4)))
```

```{r}
f2 = susie_suff_stat(XtX = d2$XtX, Xty = d2$Xty, yty = d2$yty, n = d2$n, L=10, track_fit = T, refine = TRUE)
susie_plot(f2, y='PIP', b=b, add_legend = T, main=paste0('ELBO: ', round(susie_get_objective(f2), 4)))
```

## Data 6

Default doesn't initialization works. LASSO initialization doesn't work.

```{r}
d6 = dat$d6
b = d6$true_coef
idx = which(b!=0)

par(mfrow=c(1,2))
plot(d6$z, pch = 16, xlab = 'SNPs', ylab = 'z')
points(idx, d6$z[idx], col='red', pch = 16)
log10p = -log10(pnorm(-abs(d6$z))*2)
plot(log10p, pch = 16, xlab = 'SNPs', ylab = '-log10 p value')
points(idx, log10p[idx], col='red', pch = 16)
```

With default initialization:
```{r}
f6 = susie_suff_stat(XtX = d6$XtX, Xty = d6$Xty, yty = d6$yty, n = d6$n, L=10, track_fit = T)
susie_plot(f6, y='PIP', b=b, add_legend = T, main=paste0('ELBO: ', round(susie_get_objective(f6), 4)))
```

```{r}
f6 = susie_suff_stat(XtX = d6$XtX, Xty = d6$Xty, yty = d6$yty, n = d6$n, L=10, track_fit = T, refine = TRUE)
susie_plot(f6, y='PIP', b=b, add_legend = T, main=paste0('ELBO: ', round(susie_get_objective(f6), 4)))
```

## Data 3

Default initialization works. LASSO initialization doesn't work.

```{r}
d3 = dat$d3
b = d3$true_coef
idx = which(b!=0)

par(mfrow=c(1,2))
plot(d3$z, pch = 16, xlab = 'SNPs', ylab = 'z')
points(idx, d3$z[idx], col='red', pch = 16)
log10p = -log10(pnorm(-abs(d3$z))*2)
plot(log10p, pch = 16, xlab = 'SNPs', ylab = '-log10 p value')
points(idx, log10p[idx], col='red', pch = 16)
```

With default initialization:
```{r}
f3 = susie_suff_stat(XtX = d3$XtX, Xty = d3$Xty, yty = d3$yty, n = d3$n, L=10, track_fit = T)
susie_plot(f3, y='PIP', b=b, add_legend = T, main=paste0('ELBO: ', round(susie_get_objective(f3), 4)))
```

```{r}
f3 = susie_suff_stat(XtX = d3$XtX, Xty = d3$Xty, yty = d3$yty, n = d3$n, L=10, track_fit = T, refine = TRUE)
susie_plot(f3, y='PIP', b=b, add_legend = T, main=paste0('ELBO: ', round(susie_get_objective(f3), 4)))
```
