---
title: "SuSiE RSS convergence problem"
author: "Yuxin Zou"
date: "3/9/2021"
output: 
  workflowr::wflow_html:
    code_folding: hide
---

We observe the convergence problem for SuSiE in simulation.

```{r}
library(susieR)
dat = readRDS('data/susie_convergence_problem6.rds')
```

## Data 1

Default initialization doesn't work. LASSO initialization works.

```{r}
d1 = dat$d1
b = d1$true_coef
idx = which(b!=0)

par(mfrow=c(1,2))
plot(d1$z, pch = 16, xlab = 'SNPs', ylab = 'z')
points(idx, d1$z[idx], col='red', pch = 16)
log10p = -log10(pnorm(-abs(d1$z))*2)
plot(log10p, pch = 16, xlab = 'SNPs', ylab = '-log10 p value')
points(idx, log10p[idx], col='red', pch = 16)
```

With default initialization:
```{r}
f1 = susie_suff_stat(XtX = d1$XtX, Xty = d1$Xty, yty = d1$yty, n = d1$n, L=10, track_fit = T)
susie_plot(f1, y='PIP', b=b, add_legend = T, main=paste0('ELBO: ', round(susie_get_objective(f1), 4)))
```
```{r}
f1 = susie_suff_stat(XtX = d1$XtX, Xty = d1$Xty, yty = d1$yty, n = d1$n, L=10, track_fit = T)
## remove SNP in CS from f1
for( cs in 1:length(f1$sets$cs)){
  pw = rep(1, length(b))
  pw[f1$sets$cs[[cs]]] = 0
  f1s2 = susie_suff_stat(XtX = d1$XtX, Xty = d1$Xty, yty = d1$yty, n = d1$n, L=10, track_fit = T, prior_weights = pw)
  sinit2 = f1s2[c('alpha', 'mu', 'mu2')]
  # sinit2 = lapply(sinit2, function(x) x[f1s2$sets$cs_index,])
  # sinit2$alpha = rbind(sinit2$alpha, f1$alpha[f1$sets$cs_index,])
  # sinit2$mu = rbind(sinit2$mu, f1$mu[f1$sets$cs_index,])
  # sinit2$mu2 = rbind(sinit2$mu2, f1$mu2[f1$sets$cs_index,])
  class(sinit2) <- c("susie","list")
  ## initialize at f1s2
  f1s3 = susie_suff_stat(XtX = d1$XtX, Xty = d1$Xty, yty = d1$yty, n = d1$n, L=10, track_fit = T, s_init = sinit2)
  susie_plot(f1s3, y='PIP', b=b, add_legend = T, main=paste0('ELBO: ', round(susie_get_objective(f1s3), 4)))
}
```

Scale XtX, Xty, yty, n by 0.5
```{r}
n0 = d1$n/2
s = n0/d1$n
f1s = susie_suff_stat(XtX = s*d1$XtX, Xty = s*d1$Xty, yty = s*d1$yty, n = n0, L=10, track_fit = T)
susie_plot(f1s, y='PIP', b=b, add_legend = T, main=paste0('ELBO: ', round(susie_get_objective(f1s), 4)))
```

With oracle initialization:
```{r}
beta_val = b[idx]
sinit = susieR::susie_init_coef(idx, beta_val, length(b))
f1true = susie_suff_stat(XtX = d1$XtX, Xty = d1$Xty, yty = d1$yty, n = d1$n, track_fit = T, s_init = sinit,
                            estimate_residual_variance = T,estimate_prior_variance = TRUE, max_iter = 200)
susie_plot(f1true, y='PIP', b=b, add_legend = T, main=paste0('ELBO: ', round(susie_get_objective(f1true), 4)))
```


## Data 2

Default initialization doesn't work. LASSO initialization doesn't work.

```{r}
d2 = dat$d2
b = d2$true_coef
idx = which(b!=0)

par(mfrow=c(1,2))
plot(d2$z, pch = 16, xlab = 'SNPs', ylab = 'z')
points(idx, d2$z[idx], col='red', pch = 16)
log10p = -log10(pnorm(-abs(d2$z))*2)
plot(log10p, pch = 16, xlab = 'SNPs', ylab = '-log10 p value')
points(idx, log10p[idx], col='red', pch = 16)
```

With default initialization:
```{r}
f2 = susie_suff_stat(XtX = d2$XtX, Xty = d2$Xty, yty = d2$yty, n = d2$n, L=10, track_fit = T)
susie_plot(f2, y='PIP', b=b, add_legend = T, main=paste0('ELBO: ', round(susie_get_objective(f2), 4)))
```

```{r}
f2 = susie_suff_stat(XtX = d2$XtX, Xty = d2$Xty, yty = d2$yty, n = d2$n, L=10, track_fit = T)
## remove SNP in CS from f2
for( cs in 1:length(f2$sets$cs)){
  pw = rep(1, length(b))
  pw[f2$sets$cs[[cs]]] = 0
  f2s2 = susie_suff_stat(XtX = d2$XtX, Xty = d2$Xty, yty = d2$yty, n = d2$n, L=10, track_fit = T, prior_weights = pw)
  sinit2 = f2s2[c('alpha', 'mu', 'mu2')]
  # sinit2 = lapply(sinit2, function(x) x[f2s2$sets$cs_index,])
  # sinit2$alpha = rbind(sinit2$alpha, f2$alpha[f2$sets$cs_index,])
  # sinit2$mu = rbind(sinit2$mu, f2$mu[f2$sets$cs_index,])
  # sinit2$mu2 = rbind(sinit2$mu2, f2$mu2[f2$sets$cs_index,])
  class(sinit2) <- c("susie","list")
  ## initialize at f2s2
  f2s3 = susie_suff_stat(XtX = d2$XtX, Xty = d2$Xty, yty = d2$yty, n = d2$n, L=10, track_fit = T, s_init = sinit2)
  susie_plot(f2s3, y='PIP', b=b, add_legend = T, main=paste0('ELBO: ', round(susie_get_objective(f2s3), 4)))
}
```

Scale XtX, Xty, yty, n by 0.1
```{r}
n0 = d2$n/10
s = n0/d2$n
f2s = susie_suff_stat(XtX = s*d2$XtX, Xty = s*d2$Xty, yty = s*d2$yty, n = n0, L=10, track_fit = T)
susie_plot(f2s, y='PIP', b=b, add_legend = T, main=paste0('ELBO: ', round(susie_get_objective(f2s), 4)))
```

We initialize at the truth,
```{r}
beta_val = b[idx]
sinit = susieR::susie_init_coef(idx, beta_val, length(b))
f2true = susie_suff_stat(XtX = d2$XtX, Xty = d2$Xty, yty = d2$yty, n = d2$n, track_fit = T, s_init = sinit,
                            estimate_residual_variance = T,estimate_prior_variance = TRUE, max_iter = 200)
susie_plot(f2true, y='PIP', b=b, add_legend = T, main=paste0('ELBO: ', round(susie_get_objective(f2true), 4)))
```

## Data 6

Default doesn't initialization works. LASSO initialization doesn't work.

```{r}
d6 = dat$d6
b = d6$true_coef
idx = which(b!=0)

par(mfrow=c(1,2))
plot(d6$z, pch = 16, xlab = 'SNPs', ylab = 'z')
points(idx, d6$z[idx], col='red', pch = 16)
log10p = -log10(pnorm(-abs(d6$z))*2)
plot(log10p, pch = 16, xlab = 'SNPs', ylab = '-log10 p value')
points(idx, log10p[idx], col='red', pch = 16)
```

With default initialization:
```{r}
f6 = susie_suff_stat(XtX = d6$XtX, Xty = d6$Xty, yty = d6$yty, n = d6$n, L=10, track_fit = T)
susie_plot(f6, y='PIP', b=b, add_legend = T, main=paste0('ELBO: ', round(susie_get_objective(f6), 4)))
```

```{r}
f6 = susie_suff_stat(XtX = d6$XtX, Xty = d6$Xty, yty = d6$yty, n = d6$n, L=10, track_fit = T)
## remove SNP in CS from f6
for( cs in 1:length(f6$sets$cs)){
  pw = rep(1, length(b))
  pw[f6$sets$cs[[cs]]] = 0
  f6s2 = susie_suff_stat(XtX = d6$XtX, Xty = d6$Xty, yty = d6$yty, n = d6$n, L=10, track_fit = T, prior_weights = pw)
  sinit2 = f6s2[c('alpha', 'mu', 'mu2')]
  # sinit2 = lapply(sinit2, function(x) x[f6s2$sets$cs_index,])
  # sinit2$alpha = rbind(sinit2$alpha, f6$alpha[f6$sets$cs_index,])
  # sinit2$mu = rbind(sinit2$mu, f6$mu[f6$sets$cs_index,])
  # sinit2$mu2 = rbind(sinit2$mu2, f6$mu2[f6$sets$cs_index,])
  class(sinit2) <- c("susie","list")
  ## initialize at f6s2
  f6s3 = susie_suff_stat(XtX = d6$XtX, Xty = d6$Xty, yty = d6$yty, n = d6$n, L=10, track_fit = T, s_init = sinit2)
  susie_plot(f6s3, y='PIP', b=b, add_legend = T, main=paste0('ELBO: ', round(susie_get_objective(f6s3), 4)))
}
```

Scale XtX, Xty, yty, n by 2
```{r}
n0 = d6$n/2
s = n0/d6$n
f6s = susie_suff_stat(XtX = s*d6$XtX, Xty = s*d6$Xty, yty = s*d6$yty, n = n0, L=10, track_fit = T)
susie_plot(f6s, y='PIP', b=b, add_legend = T, main=paste0('ELBO: ', round(susie_get_objective(f6s), 4)))
```

We initialize at the truth,
```{r}
beta_val = b[idx]
sinit = susieR::susie_init_coef(idx, beta_val, length(b))
f6true = susie_suff_stat(XtX = d6$XtX, Xty = d6$Xty, yty = d6$yty, n = d6$n, track_fit = T, s_init = sinit,
                            estimate_residual_variance = T,estimate_prior_variance = TRUE, max_iter = 200)
susie_plot(f6true, y='PIP', b=b, add_legend = T, main=paste0('ELBO: ', round(susie_get_objective(f6true), 4)))
```

## Data 3

Default initialization works. LASSO initialization doesn't work.

```{r}
d3 = dat$d3
b = d3$true_coef
idx = which(b!=0)

par(mfrow=c(1,2))
plot(d3$z, pch = 16, xlab = 'SNPs', ylab = 'z')
points(idx, d3$z[idx], col='red', pch = 16)
log10p = -log10(pnorm(-abs(d3$z))*2)
plot(log10p, pch = 16, xlab = 'SNPs', ylab = '-log10 p value')
points(idx, log10p[idx], col='red', pch = 16)
```

With default initialization:
```{r}
f3 = susie_suff_stat(XtX = d3$XtX, Xty = d3$Xty, yty = d3$yty, n = d3$n, L=10, track_fit = T)
susie_plot(f3, y='PIP', b=b, add_legend = T, main=paste0('ELBO: ', round(susie_get_objective(f3), 4)))
```

```{r}
f3 = susie_suff_stat(XtX = d3$XtX, Xty = d3$Xty, yty = d3$yty, n = d3$n, L=10, track_fit = T)
## remove SNP in CS from f3
for( cs in 1:length(f3$sets$cs)){
  pw = rep(1, length(b))
  pw[f3$sets$cs[[cs]]] = 0
  f3s2 = susie_suff_stat(XtX = d3$XtX, Xty = d3$Xty, yty = d3$yty, n = d3$n, L=10, track_fit = T, prior_weights = pw)
  sinit2 = f3s2[c('alpha', 'mu', 'mu2')]
  class(sinit2) <- c("susie","list")
  ## initialize at f3s2
  f3s3 = susie_suff_stat(XtX = d3$XtX, Xty = d3$Xty, yty = d3$yty, n = d3$n, L=10, track_fit = T, s_init = sinit2)
  susie_plot(f3s3, y='PIP', b=b, add_legend = T, main=paste0('ELBO: ', round(susie_get_objective(f3s3), 4)))
}
```

Scale XtX, Xty, yty, n by 2
```{r}
n0 = d3$n/2
s = n0/d3$n
f3s = susie_suff_stat(XtX = s*d3$XtX, Xty = s*d3$Xty, yty = s*d3$yty, n = n0, L=10, track_fit = T)
susie_plot(f3s, y='PIP', b=b, add_legend = T, main=paste0('ELBO: ', round(susie_get_objective(f3s), 4)))
```

We initialize at the truth,
```{r}
beta_val = b[idx]
sinit = susieR::susie_init_coef(idx, beta_val, length(b))
f3true = susie_suff_stat(XtX = d3$XtX, Xty = d3$Xty, yty = d3$yty, n = d3$n, track_fit = T, s_init = sinit,
                            estimate_residual_variance = T,estimate_prior_variance = TRUE, max_iter = 200)
susie_plot(f3true, y='PIP', b=b, add_legend = T, main=paste0('ELBO: ', round(susie_get_objective(f3true), 4)))
```
